Wavelet Spatio-Temporal Change Detection on multi-temporal SAR images

### 2021-11-09 tex/paper.wecs/wecs_tgrs.tex
files to draw a diagram
Computing SNR for simulated and real data

The time points with highest values of $\vd(m)$ represent the images for which the most expressive changes take place, where changes here are measured through $\mathbb{L}_2$ energy. Define the  $n\times p$ matrix
\begin{equation*}
 \vD=\left(
 \begin{array}{c}
 vec(\vD(1))^T\\
 \vdots\\
 vec(\vD(n))^T\\
 \end{array}
 \right),
\label{eq_defmatrixD}
\end{equation*}
where $vec(\vD(m))$ is the $p\times 1$ vector of wavelet coefficients for time $m$ and $p=\#\{k,l\}$ is total number of locations represented by $\vX(m)$, $m=1,\ldots,n$. Sparsity \cite{johnstone2009statistical} on wavelet coefficients plays a special role here.  We suppose a handful of coefficients drive the changes given by $\vd$, so that the effective dimension of $\vD$ (number of locations where relevant changes occur), say $s_d$, is such that $s_d<<p$. This can be represented as the following linear model
\begin{equation} 
\vd=\vD\vbeta+\vxi
\label{E:sparsemodel_d}
\end{equation}
where $\vbeta$ is sparse, i.e., it has $p-s_d$ null elements, and $\vxi^{(d)}$ is some $n\times 1$ random vector of errors.
%\citep{jonhstone2009}

@@

@@

The comparison of performance for the two change detection measures considered here can be checked in Figure \ref{F:forest_roc_wecs_agg}, where a ROC curve is computed to check the correct detection of changes. The reference of correct change regions is shown in Figure \ref{F:forest_roc_wecs_agg}a, which are determined using [XXXXX]. We can also compare the change detection methods using the $F_1$-score accuracy measure. Denoting $\mathrm{TP}$ as the number of true positives (change pixels correctly detected), $\mathrm{FP}$ as the number of false positives (nonchange pixels flagged as change point) and $\mathrm{FN}$ as the total of false negatives (change points flagged as nonchange point), the $F_1$-score is defined as
\begin{equation*}
F_1 = 2\frac{\mathrm{Pr}\cdot\mathrm{Re}}{\mathrm{Pr}+\mathrm{Re}}	,
\end{equation*}
where
\begin{equation*}
\mathrm{Pr}=\frac{\mathrm{TP}}{\mathrm{TP}+\mathrm{FP}}\quad 
\text{and} \quad \mathrm{Re} = \frac{\mathrm{TP}}{\mathrm{TP}+\mathrm{FN}}.
\end{equation*}
Results of these three accuracy measures are presented in Table \ref{T:forest_accuracy}. Results for aggregation of absolutes differences correspond to two types of thresholds: Otsu's method and Kittler-Illingworth \cite{kittler1986minimum}. We can observe that WECS presents the highest value of $F_1$-score, which means it has a better performance that the competing method.

@@

We present a novel way of detecting changes in multi-temporal satellite images, WECS. The procedure is based on wavelet energies from both the estimated individual coefficients as well as the whole mean image. It makes use of correlation screening for ultra-high dimensional data. The proposed method's performance is shown using both simulated and real data. The proposed method is useful to detect spatio-temporal change points, which is illustrated on data analyses. The method is employed to analyze a time series of 84 images of a forest.

>>>>

The time points with highest values of $\vd(m)$ represent the images for which the most expressive changes take place, where changes here are measured through $\mathbb{L}_2$ energy. Define the  $n\times p$ matrix
\begin{equation*}
 \vD=\left(
 \begin{array}{c}
 vec(\vD(1))^T\\
 \vdots\\
 vec(\vD(n))^T\\
 \end{array}
 \right),
\label{eq_defmatrixD}
\end{equation*}
where $vec(\vD(m))$ is the $p\times 1$ vector of wavelet coefficients for time $m$ and $p=\#\{k,l\}$ is total number of locations represented by $\vX(m)$, $m=1,\ldots,n$. Sparsity \cite{johnstone2009statistical} on wavelet coefficients plays a special role here.  We suppose a handful of coefficients drive the changes given by $\vd$, so that the effective dimension of $\vD$ (number of locations where relevant changes occur), say $s_d$, is such that $s_d<<p$. This can be represented as the following linear model
\begin{equation} 
\vd=\vD\vbeta+\vxi
\label{E:sparsemodel_d}
\end{equation}
where $\vbeta$ is sparse, i.e., it has $p-s_d$ null elements, and $\vxi^{(d)}$ is some $n\times 1$ random vector of errors.

@@

\begin{figure}[htb!]
\centering
\includegraphics[scale=.45]{../../drawio/diagram_wecs.drawio}
\caption{Diagram of steps performed on WECS to compute an absolute correlation of a single point.}
\label{F:EllipsoidChanges}
\end{figure}

@@

The comparison of performance for the two change detection measures considered here can be checked in Figure \ref{F:forest_roc_wecs_agg}, where a ROC curve is computed to check the correct detection of changes. WECS attains high true positive rates before the aggregation method, but both methods design competitive results. This performance differs from the ROC curve results in the previous section because the real images have a mean signal to noise ratio (SNR) of 3.9327, whereas the simulated images were generated with SNR of 0.2309. Hence, WECS is expected to have performance closer to the aggregation method in less noisy applications. The reference of correct change regions is shown in Figure \ref{F:forest_roc_wecs_agg}a, which are determined using [XXXXX].

We can also compare the change detection methods using the $F_1$-score accuracy measure. Denoting $\mathrm{TP}$ as the number of true positives (change pixels correctly detected), $\mathrm{FP}$ as the number of false positives (nonchange pixels flagged as change point) and $\mathrm{FN}$ as the total of false negatives (change points flagged as nonchange point), the $F_1$-score is defined as
\begin{equation*}
F_1 = 2\frac{\mathrm{Pr}\cdot\mathrm{Re}}{\mathrm{Pr}+\mathrm{Re}}	,
\end{equation*}
where
\begin{equation*}
\mathrm{Pr}=\frac{\mathrm{TP}}{\mathrm{TP}+\mathrm{FP}}\quad 
\text{and} \quad \mathrm{Re} = \frac{\mathrm{TP}}{\mathrm{TP}+\mathrm{FN}}.
\end{equation*}
Results of these three accuracy measures are presented in Table \ref{T:forest_accuracy}. Results for aggregation of absolutes differences correspond to two types of thresholds: Otsu's method and Kittler-Illingworth \cite{kittler1986minimum}. We can observe that WECS presents the highest value of $F_1$-score, which means it has a better performance that the competing method.

@@

We present a novel way of detecting changes in multi-temporal satellite images, WECS. The procedure is based on wavelet energies from both the estimated individual coefficients as well as the whole mean image. It makes use of correlation screening for ultra-high dimensional data. Thereupon, WECS is expected to provide a sample of points in space in a way that such set, contains real change points with high probability. The proposed method's performance is shown using both simulated and real data. The proposed method is useful to detect spatio-temporal change points, which is illustrated on data analyses. The method is employed to analyze a time series of 84 images of a forest.
